Interactive Checks for Coordination Avoidance

### 2019-08-18 doc/vldb_slides/sections/iclosure.tex
More slide tweaks.

  \note{%
    Now that we've defined invariant confluence, we can turn our attention to
    the main goal of our paper. And that is to develop an invariant-confluence
    decision procedure. Determining whether or not a distributed object is
    invariant confluent is not easy to do by hand, so we'd like to develop a
    decision procedure that can automatically check whether something is
    invariant confluent for us.
  }
\end{frame}

@@

  \note{%
    Turns out, this is not a coincidence. An invariant confluent object may not
    be invariant closed but only because we're merging points that are
    unreachable. If the invariant is a subset of the reachable states, then
    invariant closure and invariant confluence are equivalent. \\[12pt]

>>>>

  \note{%
    Now that we've defined invariant confluence, we can turn our attention to
    the main goal of our paper. And that is to develop an invariant-confluence
    decision procedure. As you saw in the previos example, determining whether
    or not a distributed object is invariant confluent is not easy to do by
    hand, so we'd like to develop a decision procedure that can automatically
    check whether something is invariant confluent for us.
  }
\end{frame}

@@

  \note{%
    Turns out, this is not a coincidence. An invariant confluent object may not
    be invariant closed but only because we're merging points that are
    unreachable. If the invariant is a subset of the reachable states---that
    is, if every invariant satisfying point is reachable---then invariant
    closure and invariant confluence are equivalent. \\[12pt]
